---
title: "Small demo of the MR.rr package"
author: "Yuexiang Peng, Zhilong Zhang"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    toc: true
    toc_float:
      toc_collapsed: true
    theme: united
vignette: >
  %\VignetteIndexEntry{Small demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a vignette for our MR-rr package. This package contains three estimators, including the naive MR-rr estimator, the MR-rr estimator, and the the MR-rr estimator with regularization. The package also contains functions to perform simulation to test the estimators. 

# The usage of the estimator function
First, we will give a example on how to use the estimator in practice with generated sample data.
```{r}
library(MR.rr)
set.seed(123)
# Generate the data
pz = 100 # the number of SNPs
px = 10 # the number of exposures
py = 10 # the number of outcomes
rank = 5 # the rank of the causal effect matrix C
Gamma = matrix(rnorm(pz * py), pz, py) # regression coefficient matrix of outcomes on SNPs
gamma = matrix(rnorm(pz * px), pz, px) # regression coefficient matrix of exposures on SNPs
Sigma_X = matrix(rnorm(px * px), px, px) 
Sigma_X = Sigma_X %*% t(Sigma_X) # use the average SE matrix of gamma across all SNPs in practice
Sigma_Y = matrix(rnorm(py * py), py, py) 
Sigma_Y = Sigma_Y %*% t(Sigma_Y) # use the average SE matrix of Gamma across all SNPs in practice

C_hat_naive = mr_rr_naive(Y=Gamma, X=gamma, r=rank, W=solve(Sigma_Y))$AB
print("This is the estimated causal effect matrix C with rank 5 by the naive MR-rr estimator:")
print(C_hat_naive)
C_hat = mr_rr(Y=Gamma, X=gamma, r=rank, Sigma_X=Sigma_X, W=solve(Sigma_Y))$AB
print("This is the estimated causal effect matrix C with rank 5 by the MR-rr estimator:")
print(C_hat)
C_hat_r = mr_rr_regularized(Y=Gamma, X=gamma, r=rank, Sigma_X=Sigma_X, 
                          regularization_rate = 1e-13, W=solve(Sigma_Y))$AB
print("This is the estimated causal effect matrix C with rank 5 by the MR-rr estimator with regularization:")
print(C_hat_r)
```

# The usage of the run_simulation function
Then, we will illustrate how to use the simulation function in this package to access the performance of our MR-rr estimator with near realistic data. To generate a reasonable simulated data, we use the GWAS-Lipid data incorporated in the package to generate the true parameters and a rank 5 causal effect matrix C from 24 dimension exposures to 10 dimension outcomes. Then we will simulate the data with the true parameters and run the naive MR-rr estimator and MR-rr estimator with regularization to compare the performance with respect to true C.


```{r}
sim_result = run_simulation(regularized = TRUE, regularization_rate = 1e-13)
bias_naive_MRrr = sim_result[[1]]
bias_MRrr_regularized = sim_result[[2]]
print("This is a demo of the output format of the run_simulation function:")
str(bias_naive_MRrr)
print("This is a summary of the entrywise bias of the naive MR-rr estimator:")
summary(unlist(bias_naive_MRrr))
print("This is a summary of the entrywise bias of the MR-rr estimator with regularization:")
summary(unlist(bias_MRrr_regularized))
```

From a rough glance, we can see that the MR-rr estimator with regularization has a smaller bias than the naive MR-rr estimator. We can also visualize the results by plotting the boxplots of the bias and the heatmaps of the bias and standard deviation by the following functions.

# The usage of the plot_boxplot function

The boxplots function takes the bias matrices of the naive MR-rr estimator and the MR-rr estimator with regularization as input and plots the boxplot of the entry-wise bias of the causal effect matrix C. 

```{r}
plot_boxplot(bias_naive_MRrr, bias_MRrr_regularized, weight_to_plot = "0.2",
             individual_plot = TRUE, rank_by = "bias")
```

From the boxplot, we can see that the MR-rr estimator with regularization has a smaller bias than the naive MR-rr estimator. Then, we use the heatmap to visualize the bias and standard deviation of each entry of the estimator comapring to the causal effect C.

# The usage of the plot_heatmap function

```{r}
plot_heatmap(bias_naive_MRrr, bias_MRrr_regularized, weight_to_plot = "0.2")
```

We see that when the IV strength is about 1.5, the MR-rr estimator with regularization has both smaller bias and smaller standard deviation comparing to the naive MR-rr estimator.

# The usage of the nonpara_bootstrap function

Finally, we test whether the bootstrap 95 percent confidence interval covers the true causal effect matrix C with about 95% probability. 

```{r}
print("The bootstrap coverage rate is:")
nonpara_bootstrap(me_weight = 0.5, regularized = TRUE, regularization_rate = 1e-13)
```














